### 2018-03-29 submission/manuscript.Rmd
add f-stat to ANOVA result reporting

***The Number of OTUs are Dependent on HiFi DNA Polymerase:***
A consistent difference in the number of OTUs, that was dependent on the HiFi DNA polymerase used was observed regardless of sub-sampling depth for fecal samples [Figure 1]. Additionally, there was a trend for lower cycle numbers (15-20) to result in less differences in the number of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA polymerases [Figure 1]. For fecal samples, all sub-sampling levels had significant differences between HiFi DNA polymerases at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. Most of the differences observed at 35 cycles were between Platinum and other HiFi DNA polymerases, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2]. Differences in the number of OTUs between HiFi DNA polymerases were identifiable at earlier cycles (25 and 30) but the sub-sampling depth had to be 5000 sequences or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1].

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same HiFi DNA polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across cycle number and sub-sampling depth [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between HiFi DNA polymerases were observed as early as 20 cycles and at as low of a sub-sampling depth as 1000 sequences in the mock community samples (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. For both cycle numbers and sub-sampling depths, the majority of  differences in the number of OTUs were between Platinum and the other HiFi DNA polymerases [Table S4]. Based on these observations in fecal and mock communities, it is clear that different HiFi DNA polymerases result in a different total number of OTUs observed within a sample.

>>>>

***The Number of OTUs are Dependent on HiFi DNA Polymerase:***
A consistent difference in the number of OTUs, that was dependent on the HiFi DNA polymerase used was observed regardless of sub-sampling depth for fecal samples [Figure 1]. Additionally, there was a trend for lower cycle numbers (15-20) to result in less differences in the number of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA polymerases [Figure 1]. For fecal samples, all sub-sampling levels had significant differences between HiFi DNA polymerases at 35 cycles (F-stat > `r round(min(filter(fs_anova_summary, cycle == "35x")[, "F.value"]), digits = 2)`, P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. Most of the differences observed at 35 cycles were between Platinum and other HiFi DNA polymerases, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2]. Differences in the number of OTUs between HiFi DNA polymerases were identifiable at earlier cycles (25 and 30) but the sub-sampling depth had to be 5000 sequences or higher (F-stat > `r round(min(filter(fs_anova_summary, cycle == "25x" | cycle == "30x", sub_sample_level != 1000)[, "F.value"]), digits = 2)`, P-value `r ifelse(max(filter(fs_anova_summary, cycle == "25x" | cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1].

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples [Figure 2]. Regardless if fecal or mock communities were used, the same HiFi DNA polymerases had high (Platinum) and low (Accuprime) number of OTUs and this was consistent across cycle number and sub-sampling depth [Figure 1-2 & Table S1-S4]. In contrast to the results obtained with fecal samples, differences between HiFi DNA polymerases were observed as early as 20 cycles and at as low of a sub-sampling depth as 1000 sequences in the mock community samples (F-stat = `r round(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "F.value"], digits = 2)`, P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. For both cycle numbers and sub-sampling depths, the majority of  differences in the number of OTUs were between Platinum and the other HiFi DNA polymerases [Table S4]. Based on these observations in fecal and mock communities, it is clear that different HiFi DNA polymerases result in a different total number of OTUs observed within a sample.

### 2018-03-29 submission/manuscript.tex
add f-stat to ANOVA result reporting

\textbf{\emph{The Number of OTUs are Dependent on HiFi DNA Polymerase:}}
A consistent difference in the number of OTUs, that was dependent on the
HiFi DNA polymerase used was observed regardless of sub-sampling depth
for fecal samples {[}Figure 1{]}. Additionally, there was a trend for
lower cycle numbers (15-20) to result in less differences in the number
of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA
polymerases {[}Figure 1{]}. For fecal samples, all sub-sampling levels
had significant differences between HiFi DNA polymerases at 35 cycles
(P-value \textless{} 0.0001) {[}Table S1{]}. Most of the differences
observed at 35 cycles were between Platinum and other HiFi DNA
polymerases, based on a Tukey post-hoc test (P-value \textless{} 0.05)
{[}Table S2{]}. Differences in the number of OTUs between HiFi DNA
polymerases were identifiable at earlier cycles (25 and 30) but the
sub-sampling depth had to be 5000 sequences or higher (P-value
\textless{} 0.05) {[}Table S1{]}.

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples {[}Figure 2{]}. Regardless
if fecal or mock communities were used, the same HiFi DNA polymerases
had high (Platinum) and low (Accuprime) number of OTUs and this was
consistent across cycle number and sub-sampling depth {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between HiFi DNA polymerases were observed as early as 20
cycles and at as low of a sub-sampling depth as 1000 sequences in the
mock community samples (P-value = 0.002) {[}Table S3{]}. For both cycle
numbers and sub-sampling depths, the majority of differences in the
number of OTUs were between Platinum and the other HiFi DNA polymerases
{[}Table S4{]}. Based on these observations in fecal and mock
communities, it is clear that different HiFi DNA polymerases result in a
different total number of OTUs observed within a sample.

>>>>

\textbf{\emph{The Number of OTUs are Dependent on HiFi DNA Polymerase:}}
A consistent difference in the number of OTUs, that was dependent on the
HiFi DNA polymerase used was observed regardless of sub-sampling depth
for fecal samples {[}Figure 1{]}. Additionally, there was a trend for
lower cycle numbers (15-20) to result in less differences in the number
of OTUs versus higher cycle numbers (25, 30, and 35) between HiFi DNA
polymerases {[}Figure 1{]}. For fecal samples, all sub-sampling levels
had significant differences between HiFi DNA polymerases at 35 cycles
(F-stat \textgreater{} 16.35, P-value \textless{} 0.0001) {[}Table
S1{]}. Most of the differences observed at 35 cycles were between
Platinum and other HiFi DNA polymerases, based on a Tukey post-hoc test
(P-value \textless{} 0.05) {[}Table S2{]}. Differences in the number of
OTUs between HiFi DNA polymerases were identifiable at earlier cycles
(25 and 30) but the sub-sampling depth had to be 5000 sequences or
higher (F-stat \textgreater{} 4.98, P-value \textless{} 0.05) {[}Table
S1{]}.

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples {[}Figure 2{]}. Regardless
if fecal or mock communities were used, the same HiFi DNA polymerases
had high (Platinum) and low (Accuprime) number of OTUs and this was
consistent across cycle number and sub-sampling depth {[}Figure 1-2 \&
Table S1-S4{]}. In contrast to the results obtained with fecal samples,
differences between HiFi DNA polymerases were observed as early as 20
cycles and at as low of a sub-sampling depth as 1000 sequences in the
mock community samples (F-stat = 15.82, P-value = 0.002) {[}Table S3{]}.
For both cycle numbers and sub-sampling depths, the majority of
differences in the number of OTUs were between Platinum and the other
HiFi DNA polymerases {[}Table S4{]}. Based on these observations in
fecal and mock communities, it is clear that different HiFi DNA
polymerases result in a different total number of OTUs observed within a
sample.
